The Ky Fan Norms and Beyond: Dual Norms and Combinations for Matrix Optimization

### 2025-12-01 article_final/main.tex
Removed redundant table

\section{More details for Linear Least Squares}
\label{sec:lls_plots_section}
Tuned \texttt{lr} and \texttt{momentum} coefficients are presented in \tableref{tbl:lls_lrs_app}. The spectral and nuclear norms of the gradients over iterations, as well as the loss over time, are shown in \figureref{fig:app_lls}. The poor performance of Fanions and F-Fanions in terms of speed for large $k$ is likely caused by the inefficient implementation of TRLan.

\begin{table}[htbp]
\floatconts
  {tbl:lls_lrs_app}
  {\caption{Tuned \texttt{lr} and \texttt{momentum} coefficients in the lease squares experiment.}}
  {%
    \begin{tabular}{|c|c|c|c|}
      \arrayrulecolor{black}\hline
      Algorithm & \texttt{lr}  & \texttt{momentum}  & Iterations to 0.001 loss \\
      \arrayrulecolor{black}\hline
      Muon & 0.007 & 0.5 & 1060 \\
      \hdashline
      NSGD & 0.08 & 0.95 & 1020 \\
      F-Muon & 0.015 & 0.7 & 910 \\
      \hdashline
      SignSGD & 0.016 $\times$ 0.01 & 0.95 & 2650 \\
      S-Muon & 0.011 & 0.9 & 890 \\
      \arrayrulecolor{black}\hline
    \end{tabular}%
  }
\end{table}

>>>>

\section{More details for Linear Least Squares}
\label{sec:lls_plots_section}
The spectral and nuclear norms of the gradients over iterations, as well as the loss over time, are shown in \figureref{fig:app_lls}. The poor performance of Fanions and F-Fanions in terms of speed for large $k$ is likely caused by the inefficient implementation of TRLan.
